% !TeX root = ../main.tex
% Add the above to each chapter to make compiling the PDF easier in some editors.

\chapter{Future work}\label{chapter:futurework}
In the following section, imaginable improvements and extensions are going to be discussed.\newline 
Starting with the incomplete app, as shown in section \ref{sec:showcase} the created model of the deep neural network actually is operable and functioning correctly. Once again, most likely the issue is some bug regarding the preprocessing of the image. It would be nice if this inadequacy would be fixed in the future, as this is very likely just a minor issue, that could not be fixed in time. \newline
Consequently, the adaption to the simulator should neither be a major problem, assumed first issue is fixed, as the functionalities vehicle detection and lane detection already possess this feature. \newline
The unsatisfactory regarding the shifting ROI, most likely could be solved by filling the contours like in subsection \ref{zynq}, before applying the Hough Transform, again this probably might not pose a very difficult task to implement. \newline
The problem concerning the amount of images for both datasets could be solved either by harvesting more images manually, or by finding an already prepared dataset. When it comes to extending the model to detect even higher speed limits, diverse modification have to be made. Initially, the folders containing the training and validation data must be extended to have new folders containing these extra pictures and having the folders named after the containing value. Then new TFRecords file have to be created. Additionally,  existing ANN, must be adjusted to having more output neurons and finally, a complete new training has to be completed.\newline


